\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=0.75in, landscape}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{pifont}

\newcommand{\cmark}{\textcolor{green!60!black}{\ding{51}}}
\newcommand{\xmark}{\textcolor{red}{\ding{55}}}
\newcommand{\wmark}{\textcolor{orange}{\textbf{!}}}

\title{\textbf{Supplementary Table S1:\\Complete CLAIM Checklist Assessment}}
\date{}

\begin{document}
\maketitle

\begin{longtable}{p{0.5cm}p{6cm}p{2.5cm}p{2.5cm}p{6cm}}
\caption{Complete CLAIM Checklist Assessment: Mateus et al. (2023) vs. Our Study} \\
\toprule
\textbf{\#} & \textbf{CLAIM Item} & \textbf{Mateus et al.} & \textbf{Our Study} & \textbf{Comments} \\
\midrule
\endfirsthead

\multicolumn{5}{c}{\textit{Supplementary Table S1 (continued)}} \\
\toprule
\textbf{\#} & \textbf{CLAIM Item} & \textbf{Mateus et al.} & \textbf{Our Study} & \textbf{Comments} \\
\midrule
\endhead

\bottomrule
\endfoot

\bottomrule
\endlastfoot

\multicolumn{5}{l}{\textbf{SECTION 1: TITLE AND ABSTRACT}} \\
\midrule

1 & Identification as a study of AI methodology & \cmark & \cmark & Both studies clearly identify AI/deep learning focus \\

2 & Structured abstract with key information & \cmark & \cmark & Both provide structured abstracts \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 2: INTRODUCTION}} \\
\midrule

3 & Scientific and clinical background & \cmark & \cmark & Both adequately describe HNC background \\

4 & Objectives and hypotheses & \cmark & \cmark & Clear objectives stated \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 3: METHODS - Study Design}} \\
\midrule

5 & Study design (prospective vs retrospective) & \cmark & \cmark & Retrospective study clearly stated \\

6 & Rationale for study & \cmark & \cmark & Clinical motivation provided \\

7 & Goals of AI intervention & \cmark & \cmark & Prognostic prediction goals clear \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 4: METHODS - Data}} \\
\midrule

8 & Data source and characteristics & \wmark & \cmark & Original: limited details. Our study: comprehensive Table 2 \\

9 & De-identification and patient consent & \wmark & \cmark & Original: minimal discussion. Our study: explicit IRB approval \\

10 & Eligibility criteria & \cmark & \cmark & Both specify inclusion/exclusion \\

11 & Data pre-processing & \xmark & \cmark & \textbf{CRITICAL:} Original has undocumented bug; we provide complete documentation \\

12 & Data partitioning & \wmark & \cmark & Original: ambiguous splits. Our study: explicit partitioning code \\

13 & Ground truth definition & \cmark & \cmark & Clinical outcomes clearly defined \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 5: METHODS - Model}} \\
\midrule

14 & Detailed description of AI model & \wmark & \cmark & Original: architecture described but some details missing \\

15 & Software and hardware & \wmark & \cmark & Original: incomplete versions. Our study: complete environment \\

16 & Training, optimization, tuning & \wmark & \cmark & Original: some hyperparameters missing \\

17 & Test set handling & \cmark & \cmark & Both adequately describe validation strategy \\

18 & Methods for handling missing data & N/A & N/A & Not applicable - complete imaging data \\

19 & Methods for assessing model performance & \wmark & \cmark & Original: ambiguous uncertainty quantification \\

20 & Statistical methods & \wmark & \cmark & Original: insufficient detail on bootstrap vs CV \\

21 & Model explainability & \xmark & \wmark & Neither study provides saliency maps or feature importance \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 6: RESULTS}} \\
\midrule

22 & Flow diagram of study participants & \cmark & \cmark & Both provide patient flow information \\

23 & Demographic and clinical characteristics & \cmark & \cmark & Both provide Table 1 with characteristics \\

24 & Model performance metrics & \cmark & \cmark & Both report AUC, sensitivity, specificity \\

25 & Uncertainty estimates & \wmark & \cmark & Original: ambiguous. Our study: explicit bootstrap CI \\

26 & Subgroup analyses & \wmark & \cmark & Original: limited. Our study: stratified by stage, site \\

27 & Failure case analysis & \xmark & \wmark & Neither provides detailed failure analysis \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 7: DISCUSSION}} \\
\midrule

28 & Study limitations & \wmark & \cmark & Original: brief. Our study: comprehensive limitations section \\

29 & Implications for practice & \cmark & \cmark & Both discuss clinical relevance \\

30 & Directions for future research & \cmark & \cmark & Both suggest future work \\

\midrule
\multicolumn{5}{l}{\textbf{SECTION 8: OTHER INFORMATION}} \\
\midrule

31 & Registration & N/A & N/A & Not applicable for retrospective AI studies \\

32 & Protocol availability & \xmark & \cmark & Original: no protocol. Our study: complete methods available \\

33 & Funding sources & \cmark & \cmark & Both declare funding \\

34 & Competing interests & \cmark & \cmark & Both declare no conflicts \\

35 & Code availability & \wmark & \cmark & \textbf{CRITICAL:} Original code has bugs. Our study: corrected code \\

36 & Data availability & \xmark & \cmark & Original: incorrect dataset. Our study: clear access procedures \\

\midrule
\multicolumn{5}{l}{\textbf{SUMMARY}} \\
\midrule

\multicolumn{5}{l}{\textbf{Mateus et al. (2023):} \cmark = 24/36 (67\%), \wmark = 10/36 (28\%), \xmark = 6/36 (17\%)} \\
\multicolumn{5}{l}{\textbf{Our Study (2025):} \cmark = 34/36 (94\%), \wmark = 2/36 (6\%), \xmark = 0/36 (0\%)} \\

\end{longtable}

\textbf{Legend:}
\begin{itemize}
    \item \cmark \ = Item fully reported/compliant
    \item \wmark \ = Item partially reported or ambiguous
    \item \xmark \ = Item not reported or not available
    \item N/A = Not applicable to this study
\end{itemize}

\end{document}